`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-06-16 inst/manuscript/manuscript.rmd
Proper description of current parameter set;

allows for the complete generation of the PPR plot in publication quality from
the user assembled spreadsheet of input data (`x`), including automatically
added graphical representations the PPR value equal to the fit constant
$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average
carrying one scramblase and 63% have one or more 
[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
adjusted to use scramblase--mediated fluorescence reduction normalized to either
the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
exponential fit to it (`scale_to = "model"`; for reasoning see above) and whether
or not to require the exponential curve fitted to the data to go through the
origin. `ppr_scale_factor` allows for the modification of scaling to account for
a pool of vesicles that is scramblase--inaccessible (see above). The
`split_by_experiment` argument is used to indicate whether independent
experiments are integrated into a single analysis
(`split_by_experiment = FALSE`) or treated separately
(`split_by_experiment = TRUE`; see below for example usage). The
`force_through_origin` parameter may be used to employ a fit with more degrees
of freedom. While the non--default `force_through_origin = FALSE` allows for a
better fit to some experimental data, its mechanistic implications are unclear.

>>>>

allows for the complete generation of the PPR plot in publication quality from
the user assembled spreadsheet of input data (`x`). The behavior of the function
may be adjusted to use scramblase--mediated fluorescence reduction normalized to
either the maximum measurement in the series (`scale_to = "data"`) or the
plateau of an exponential fit to it (`scale_to = "model"`; default; for
reasoning see above). `ppr_scale_factor` allows for the modification of scaling
to account for a pool of vesicles that is scramblase--inaccessible (see above).
The formula to which the data is fitted has evolved over time and `flippant`
supports both the original (@menon_opsin_2011; @goren_constitutive_2014; `generation_of_algorithm = 1`), as well as the more recent iteration (@ploier_perturbed_submitted; default; `generation_of_algorithm = 2`), which
takes into account the size distribution of the liposome polulation used and
thus also requires parameters for liposome radius and its standard deviation 
(`r_bar` and `sigma_r_bar`, respectively; in nm, both). The
`split_by_experiment` argument is used to indicate whether independent
experiments are integrated into a single analysis
(`split_by_experiment = FALSE`) or treated separately
(`split_by_experiment = TRUE`; see below for example usage). The
`force_through_origin` parameter may be used to employ a fit with more degrees
of freedom. While the non--default `force_through_origin = FALSE` allows for a
better fit to some experimental data, its mechanistic implications are unclear.
